Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-03-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Latex table cleanup

The gypsum wallboard used in these experiments is referred to as "regular" as opposed to a gypsum wallboard `Type C' or `Type X' which are used in fire rated assemblies.   The gypsum wallboard used in these experiments was purchased from same manufacturer in an effort to have the most similar panels for use between the experiments.  The physical features of the gypsum wallboard panels are given in the table below.

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline Density (kg/m$^3$)  & Thermal Conductivity   & Specific Heat  &  &  \\ 
		\hline   & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
		\hline 807  & 24 	& 0.14 	&  		& 1.09 \\ 
		\hline  	& 100 	& 0.15  &  		&  \\ 
		\hline  	&  &  &  &  \\ 
		\hline 790 	& 20 	& 0.18	& 20 	& 0.90 \\ 
		\hline  	& 100 	& 0.15 	& 100 	& 0.90 \\ 
		\hline  	& 200 	& 0.13 	& 200 	& 0.80 \\ 
		\hline  	& 500 	& 0.15 	& 500	& 0.90 \\ 
		\hline 
		\end{tabular} 
		\caption[Thermal properties for 12.7~mm gypsum wallboard]{Thermal properties for 12.7~mm gypsum wallboard}
		\label{tab:Gypsum wallboard_Thermal_Properties}
		\end{table}

>>>>

The gypsum wallboard used in these experiments is referred to as ``regular'' as opposed to a gypsum wallboard `Type C' or `Type X' which are used in fire rated assemblies.   The gypsum wallboard used in these experiments was purchased from same manufacturer in an effort to have the most similar panels for use between the experiments.  The physical features of the gypsum wallboard panels are given in the table below.

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline Density & \multicolumn{2}{c|}{Thermal Conductivity}   & \multicolumn{2}{c|}{Specific Heat}  \\ 
		\hline (kg/m$^3$) & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
		\hline 807  & 24 	& 0.14 	&  		& 1.09 \\ 
		\hline  	& 100 	& 0.15  &  		&  \\ 
		\hline 790 	& 20 	& 0.18	& 20 	& 0.90 \\ 
		\hline  	& 100 	& 0.15 	& 100 	& 0.90 \\ 
		\hline  	& 200 	& 0.13 	& 200 	& 0.80 \\ 
		\hline  	& 500 	& 0.15 	& 500	& 0.90 \\ 
		\hline 
		\end{tabular} 
		\caption[Thermal properties for 12.7~mm gypsum wallboard]{Thermal properties for 12.7~mm gypsum wallboard}
		\label{tab:Gypsum wallboard_Thermal_Properties}
		\end{table}
